---
title: "Google Summer of Code 2021"
author: "Saurabh Tiwari"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Organisation: The R Project for Statistical Computing

### Project: Enhancing the Functionality and Accuracy of the VedicDateTime R Package


#### Easy Test

Code to return the name of the Shaka Samvatsar for a given Julian day number and maasa number:

```{r}
jd <- gregorian_to_jd(17, 6, 2022) #Julian day number
# Number associated with the masa
masa_num <- masa(gregorian_to_jd(17, 6, 2022), c(15.34, 75.13,+5.5))[1]
get_samvatsara_name(jd, masa_num)

```

Code to return Ritu’s name from a Masa.
```{r}
masa_num <- masa(gregorian_to_jd(17, 6, 2022), c(15.34, 75.13, +5.5))[1]
get_ritu_name(masa_num)

```

#### Hard Test

For the final test, I created a R package called `Calculator`. It contains five functions, `add()`, `substract()`, `multiply()`, `divide()` and `modulo()` , with documentation and tests. Then, using `devtools::check()`, I checked for any errors or warning, and uploaded the source file to <https://win-builder.r-project.org/>. It passed without errors/warnings/note.

The result of [\<https://win-builder.r-project.org/\>](https://win-builder.r-project.org/){.uri} is included in the github repository(`00check.log`).

